%
% file biblio.tex
%
\bibitem{rdup1} B. Foy, E. I. Dupont de Nemours and Co., private communication

\bibitem{rbrook1} M. Mapes and W.J. Leonhardt, J. Vac. Sci. Tech. A 11(4),
Jul/Aug 1993

\bibitem{rbrook2} W.J. Leonhardt and M. Mapes, BNL-48238

%\bibitem{rbogdan} B. Wojtsekhowski, private communication

\bibitem{rllnl2} T.T. Chiao, C.C. Chiao, and R.J. Sherry, Fracture Mechanics
and Technology, Vol. 1, 257-269 (1977)

\bibitem{rnasa} NASA Langley Materials Science Division, private communication

\bibitem{rnswc} H. Peritt, NSWC Report AD-B030932L

\bibitem{rbrook3} Occurrence Report, Brookhaven National Laboratory, 1995

\bibitem{rllnl}  S.L. Phoenix and E.M. Wu, LLNL Report, 1983

\bibitem{bi:yan1} C. Yan, {\em et al.}, ``Preliminary User's Manual for the High 
Momentum Spectrometer at JLab," JLab-R-92-002 (1992)

\bibitem{bi:hms1} HMS Superconducting Magnet Safety Review - Quadrupoles (1994)

\bibitem{bi:yan2} C. Yan, ``HMS Upgrade - The Third Order Correction," 
JLab-TN95-016 (1995)

\bibitem{bi:oxf1} Oxford Instruments User Manual Section 4.0, 
``Unpacking and Installation".

\bibitem{bi:oxf2} Oxford Instruments Tech. Manual Section 8.12,
``HMS Quadrupole Interlock Test".

\bibitem{bi:danf} Danfysik Magnet Power Supply 8000 Section 5,``Maintenance".

\bibitem{bi:hms2} HMS Superconducting Magnet Safety Review - Dipole (1994)

%\bibitem{bi:arr95} J. Arrington, ``Safety Assessment Document for the Counting 
%Room C Electronics"

\bibitem{bi:tank} M.~Hoegerl, P.~Hood, and J.~H.~Mitchell,
``Results of Hydrostatic Testing of the HMS Cerenkov Tank"

\bibitem{bi:wind} C.~D.~Cothran, M.~Hoegerl, P.~Hood, and J.~H.~Mitchell,
``Results of Safety Testing for the HMS Cerenkov Tank Windows"

\bibitem{bi:kross} B. Kross, Gas Handling System Writeup and Operator's Manual.

\bibitem{bi:Smythe}W.R. Smythe, ``JLab Hall C SOS Gas \v{C}erenkov
Detector Handbook.''  University of Colorado, Boulder, Colorado.

\bibitem{bi:Woodin}Dale Woodin, ``Conceptual Design of a Gas
\v{C}erenkov Counter for the SOS Project.''  Western Michigan
University, Kalamazoo, Michigan.

% hydrogen properties

\bibitem{bi:mc75} R.D. Mc Carty, "Hydrogen Technology Survey: Thermophysical
Properties," N76-11297, NBS 1975

%helium properties

\bibitem{bi:mc72} R.D. Mc Carty, "Thermophysical Properties of $^4$He from
2 to 1500 K with Pressures to 1000 Atmospheres," COM 75-10334, NBS 1972

\bibitem{bi:gi67} R.M. Gibbons and D.I. Nathan, " Thermodynamic Data
of $^3$He ," Tech Report AFML-TR-67-173, Oct 1967

\bibitem{bi:test} B. Terburg, " Target Cell Pressure Test Results"

\bibitem{bi:bates} W. Schmitt and C. Williamson " Boiloff Rates of
Cryogenic Targets Subjected to Catastrophic Vacuum Failure,"
Bates Internal Report \# 90-02, Sept 1990

\bibitem{bi:tgts} J. H. Mitchell, "Specifications for the Control System of
the Hall C Cryogenic Targets"

%\bibitem{bi:osp} J.H. Mitchell, R. Ent, and C.E. Keppel, "Operational
%Safety Procedure for Hall C"

\bibitem{bi:ctest} C. D. Cothran, D. Day, and J. H. Mitchell,
``Temporary Operating Safety
Procedure for the HMS Cerenkov Detector Pressure Testing"

\bibitem{bi:rbrook}M. Mapes and W.J. Leonhardt, J. Vac. Sci. Technol. A, Vol.
11, No. 4, Jul/Aug 199

%\bibitem{bi:saf} J. H. Mitchell, "Safety Assessment Document for the Hall C
%Cryogenic Targets"


