%
% file glossary.tex
%
\begin{description}
\item{Beamline physicist} - A physicist responsible for creating a beamline design
to meet the desired
beam parameters such as particle type, intensity, and backgrounds. The
beamline physicist
specifies all beamline components such as magnets, collimators, instrumentation.

\item{Safety Warden} - A individual assigned to each building who is responsible
for ensuring a safe
working environment within the building.

\item{Conduct of Operations (COO)} - A Department Of Energy Order (DOE 5480.19)
that specifies
requirements for operating a facility to ensure the safety of on-site
personnel and the general
public. (See the relevant COO posted at 
\htmladdnormallink{http://www.jlab.org/Hall-C/document}{http://www.jlab.org/Hall-C/document})

\item{EPICS} - The beamline / slow controls system used in the JLab Physics and
Accelerator
Divisions. See \htmladdnormallink{http://epics.aps.anl.gov/asd/controls}
{http://epics.aps.anl.gov/asd/controls}.

\item{Hazard Assessment} - A description of hazards and potential consequences
when no credit is
taken for active controls on the hazards.

\item{Liaison Physicist} - A physicist familiar with an experiment who is the
primary contact person
with Physics division. Represents the experiment at Physics division
planning meetings.

\item{LOTO} -  Lockout Tagout

\item{MSDS} - Material Safety Data Sheet. Required document for all chemicals
used. Describes
toxic, hazardous and flammability aspects of the chemical.

\item{ODH} - Oxygen deficiency hazard. Term used to describe a condition where the
oxygen level
may fall below 19\%, due to oxygen-displacing gases.

\item{Radiation Control Officer}  - An individual who acts on behalf of a division
head in all aspects of radiation safety.

\item{Running condition} - A document that specifies the mode of beamline
operation and imposes
limits on beam intensity, magnet current interlocks and currents, radiation
monitor interlocks,
and gate/fence configuration.

\item{Experiment Safety Assessment Document (ESAD)} - A document that describes how all the
hazards in the
experiment are controlled.
\end{description}
