%
% the file charge.tex
%

The EH\&S/QA Review Committee is responsible for reviewing mechanical, electrical, 
flammable gas, fire protection, ODH and radiation safety aspects of all experiments. In 
addition, the committee is responsible for coordinating reviews of any cryogenic systems 
by existing cryogenics safety panels. ``Experiment" is defined as all detector components 
and associated support equipment. The Committee shall review the systems indicated on 
the appropriate Preliminary Hazard Assessment spreadsheets for the hazards which are 
shown against applicable standards and ensure that proper analysis and documentation
exists. The Committee shall review Quality Assurances aspects of these experiments 
during the course of the EH\&S reviews such as ensuring good engineering design, 
practices and documentation exists.

Additional systems or items identified by the Committee, the Physics division head or 
Senior Safety Officers of the Physics division shall also be reviewed.  The Committee is 
free to combine several system reviews into one report (i.e. all systems having 
conventional electrical hazards may be completed in a single review.).

A ``design review" shall be performed at or near the conclusion of the design stage of each 
new system or modified previously used system. An ``operating review" shall be 
performed prior to initial operation of each system. The Committee may elect to perform 
additional reviews for particularly complex or hazardous systems. The results of these 
reviews shall be communicated to the head of the Physics division in a report which 
contains the following documentation:


\begin{itemize}
\item A summary report of the compliance status of the system, recommendations for  
correcting deficiencies or approving operation, and recommendations for modification to 
the SAD. The summary report should include references to applicable standards and 
should clearly indicate which items were reviewed. The summary report should also 
include the results of cryogenic system reviews performed by existing cryogenic safety 
panels


\item All supporting documentation such as checklists, calculations and notes.
\end{itemize}

	The summary report and supporting documentation will be retained in the Physics 
division Office experiment files. Radiation safety reviews shall satisfy the requirements 
of the JLab Radiological Control Manual. A EH\&S Review Coordinator will be 
assigned to each experiment. The Review Coordinator will monitor the design, 
construction and installation phases of the experiment and contact the Committee chair at 
least two weeks prior to any needed review. The Committee may request supplemental 
assistance from the Physics division to complete these reviews in a timely fashion.



