\infolevone{
\section{The Solid Target Ladder}

The scattering chamber has two target ladders associated with it,
a cryogenic target ladder and a solid target ladder. To change
from the cryogenic target ladder to the solid target ladder, one has
to:

\begin{itemize}
\item{Move the cryogenic target ladder to its home position.}
\item{Rotate the cryogenic target ladder over 90 degrees. This removes
the cryotargets from the beam line, and moves them out of the spectrometer
acceptances.}
\item{Insert the solid target ladder and select the appropriate target.}
\end{itemize}

\noindent To install the cryogenic target ladder again, one has to reverse the
process:

\begin{itemize}
\item{Move the solid target ladder to its home position (completely out
of the way).}
\item{Rotate the cryogenic target ladder back into place (-90 degree
rotation).}
\item{Select the appropriate target.}
\end{itemize}

We have four different solid target systems currently in use in the
Hall C Scattering Chamber.  There is a solid target attached directly
to the cryotarget and three versions of the independent solid target
ladder system.

The solid target that is attached to the bottom of the cryotarget is
often referred to as the optic target.  This target is a system of
aluminum and carbon foils arranged at different locations and heights
relative to the beam.  The foils provide cryotarget window
calibration and loop target spectrometer optics calibration.  The
various targets are brought into the beam by simply closing the
vertical height of the cryotarget stand and a ``scan'' can be made
that spans the length of the cryotarget in discrete steps on window
convection data taken.  This system replaced the earlier ``slanted
target'' system.

The independent solid target system has three different ladders which
mount interchangeably to the same mechanism.  This mechanism
provides for a telescopic guidance system with good accuracy
and stability as well as vertical, and rotary control.  The rotary mechanism also
has an integral rotary water feed thru for high power solid target
runnings. 

The three solid target ladders use identically sized interchangeable
variable thickness solid targets.  They use a common target mounting
system.  The three ladders currently available are:

\begin{itemize}
\item{Un-cooled target ladder with a standard solid target position.
This is for 0-30 $\mu$A rastered beams for materials with good
conductivity and high melting points.}
\item{Water cooled target ladder with 6 standard solid target
positions.  This is for 0-100 $\mu$A beams that are rastered.  These
can handle any material.}
\item{Combination water cooled solid and water target.  This target
has, in addition to 5 solid target positions, a new water cell.
The water cell is 1 cm thick and has entrance and exit windows of 0.1
mm (~.005 in) aluminum.  The water cell is all machined and welded to
the bottom of the solid target ladder.}
\end{itemize}

In some cases the solid targets will be cooled with water to prevent
destruction of the targets by a high current beam. If this is the case
make sure that the
cooling water is indeed flowing before the experiment starts.
{\sl Failure to do so may cause loss of the targets}. Often we
do not have to use water cooling. This is the case when we are
rastering the beam, or are dealing with solid target
materials with excellent thermal conductivities (like pyrollytic
graphite or ceramic BeO) and currents less than or equal to 30 $\mu$A.

In all cases, as we may use these targets in conjunction with a high
energy, high current beam a large level of radiation may be induced
in these targets.

The main safety issue concerning the non-special targets is that
they will be radioactive (``hot") after they have been
exposed to the JLab beam for an experiment.
Targets may not be removed from the target chamber ot transported from the Hall without 
concurrence by the RCG. An SRWP specifies the requirements for target removal and/or 
transport. Targets which have been surveyed and released by the RCG will be stored in a 
second fire safety cabinet which has been designated for target storage and is located in 
the hall.

Since the targets may be water cooled, we will induce a slight
radioactive level in the cooling water. However, the cooling water
system is a closed loop, and calculations performed by the Radiation
Safety group indicate that the radioactive level induced is minimal.
Also, to ensure that the cooling water is indeed a contained system
and can not leak out to the environment, the pumping system causing
the water to flow is placed in a tray.

\subsection{Special Targets}

Some of the solid targets require special attention. In some cases
mishandling of the targets is relatively innocent, like in the case
of the natural {\bf Calcium} target. This material, when exposed to air,
will oxidize, resulting in a large oxygen content in the target.
Store natural Calcium always in an argon-filled or vacuum closed
case, or in an oil solution. Calcium can be handled in air for a limited
amount of time (a few hours) if handled with a layer of oil.

Other special targets may pose a safety concern. At this
moment the only twos special target materials we own are ceramic
{\bf Beryllium-Oxide (BeO)} and {\bf Beryllium (Be)}.
In solid form, BeO is completely safe under normal conditions of use.
The product can be safely handled with bare hands.
However, in powder form all Beryllia is {\bf toxic} when airborne.
{\bf Overexposure to airborne Beryllium particulate may cause a
serious lung disease called Chronic Berylliosis. Beryllium has also
been listed as a potential cancer hazard. Furthermore exposure to
Beryllium may aggravate medical conditions related to airway systems
(such as asthma, chronic bronchitis, etc.).}
Since beryllia are mainly dangerous in powdered form, do not machine,
break, or scratch these products. Machining of the Beryllia can only
be performed after consulting the EH\&S staff.
It is good practice to wash your
hands after handling the ceramic BeO. If handling the pure Beryllium
target wear gloves and an air filter mask.

\subsection{Storage}

The targets {\bf must} be stored in a safe, locked place tagged with the
appropriate radiation signs. At this moment we use a small yellow
fire safety cabinet for this purpose. The cabinet is stored in the
little backroom of the Hall~C counting house. The key of the target
storage cabinet can be found in the Hall~C key box, hanging on the
wall next to the Hall~C counting house entrance.
Targets may not be removed from the target chamber or transported from the hall without 
concurrence by the RCG.  An SRWP in the counting house specifies the requirements for 
target removal and/or transport.  Targets which have been surveyed and released by the 
RCG will be stored in a second fire safety cabinet placed downstairs in Hall~C,
that has been designated for target storage.

Since we will typically have
Be and/or BeO targets stored in this cabinet too, also signs indicating
the presence of Beryllium materials (``Beryllium Storage")
are tagged to this cabinet. The Material
Safety Data Sheets for Beryllia are included in the storage cabinet.



\section{Bremsstrahlung Radiator}

The Bremsstrahlung radiator consists of a target ladder with
several thicknesses of natural Cu of size 1.5" times 0.75".
Typical radiator thicknesses are 2\%, 4\%, and 6\%, all in
radiation lengths. The Bremsstrahlung radiator is the last element
in the Hall~C beamline before the scattering chamber, at a distance
of about 1.2 meter from the physics targets.

The target ladder can be moved in and out of the beam by use of
a stepping motor. Targets are cooled with water to prevent destruction
of the targets by a high current beam.
Because we may use these radiator targets in conjunction with a high
energy, high current beam we may produce a large amount of background
in the radiator, and radiation in the parts around the radiator.
For this reason the Bremsstrahlung radiator will be enclosed by a lead
shield.

The only safety issue concerning the Bremsstrahlung radiator is that of
induced radioactivity in
the Cu targets, or more seriously, in the water used for cooling the targets.
 The water cooling system is a closed loop. The heart of the system is
a portable welding torch water cooler. This device is kept in a tray
which is intended to provide secondary containment in case of a leak.
 The cooling system must not be breached or drained without concurrence from the RCG.  
Accidental breach or spill constitutes a radiation contamination hazard.  A spill control kit, 
capable of containing a system leak or spill, is staged in the hall next to the cooling system 
tray.  The cooling system is located    .

The Cu targets will certainly be activated in the course of an experiment.
Therefore, only remove
the Cu target, the target ladder, the shielding around the radiator,
and/or the whole radiator system in the presence of a Radcon technician.

\paragraph{Radiator Control}

In one of the xterm windows, type the following:

\texttt{\\
	cd ~cdaq/bin\\
	Radcontrol\\
}

and use the menu session to control the motion of the
Bremsstrahlung radiator.

The source code can be found in:

\texttt{cd \textasciitilde{}cdaq/bin/Rad\_source}

Do not change the source code without consulting
%Dave Meekins or
one of the JLab Hall~C staff.
}
