\infolevone{
A distributed computer system
based on the
Experimental Physics and Industrial Control System
(EPICS)~\cite{EPICSwww}
%\htmladdnormallinkfoot{}{\url{http://www.aps.anl.gov/epics}}
 architecture monitors and commands
various Hall C systems and the accelerator.
The basic components of the system are:
\begin{itemize}
\item Input/Output Controllers (IOCs) - Systems containing single
board computers (SBCs) and I/O modules
(i.e analog-to-digital converters (ADCs), digital I/O and RS-232C interfaces).
Each SBC executes the real-time operating system VxWorks and the corresponding EPICS application (signal database
and sequencers).  IOCs are typically VME SBCs and crates, but may also
be other platforms such as standard Linux servers or small form factor
systems such as Raspberry PIs.
\item Operator Interfaces (OPI) - Computers capable of executing
EPICS tools to interact with the IOCs.
The four most used tools in Hall C are (a)
the Extensible Display Manager (EDM)~\cite{EDMwww},
(b) StripTool, (c) a signal archiver, and (d) an alarm handler.
EDM is the main interface used for monitoring and controlling both the hall and accelerator
equipment. StripTool allows to monitor
the behavior of one or more signals as a function of time.
The signal archiver keeps a record of a selected set of signals.  The
alarm handler alerts operators to situations requiring attention.
\item Boot Servers - IOCs load the various
software components needed to perform their functions from these machines (i.e. operating system,
signal database and controls algorithms).
%\item MEDM Servers - OPI computers obtain the framework of each MEDM screen from these machines.
%\item Local Area Network (LAN) - the communication path joining the IOCs, OPIs and various servers.
\end{itemize}

In addition to equipment controlled with EPICS, Hall C uses an industrial
control system, composed of Allen Bradley PLCs (Programmable Logic
Controllers) and commercial OPI software.  This system is used to
control the cryogenics, magnets and motion of the HMS and SHMS
spectrometers.  This system is described in
section~\ref{sec:spectrometercontrols}.  The system includes an interface to
EPICS making spectrometer information available to standard EPICS tools and
to give the PLC based control systems access to cryogenic plant information
available in EPICS.

} %\infolevone
\obsolete{ % comment out until in better shape
%\infolevfour{
\section{System's Components}

Need to be careful not to put information here that quickly goes out
of date.  Refer to howtos for EPICS build directory, HV configuraion
and operation

Basic description of EPICS.

Note that used to display information about accelerator status and to
display and control Hall C equipment such as targets and high voltage.

Describe logging of EPICS information.   Information logged by
accelerator.  Instructions on how to add signals to logging.  How to
display logged information.

Note that EPICS information is recorded in CODA data stream.

Account used for EPICS.  Location of control screens.

Refer to target chapter and target operating manual for target controls.

Note that spectrometer magnet and angle setting does not use EPICS.
Refer to spectrometer chapter for information on that control system.
Note that spectrometer information is availabe as readonly EPICS so
that spectrometer information can be read, displayed and logged with
EPICS tools.

List the following EPICS Systems
  High Voltage control -> HV section
  Target Controls -> Target Chapter
  Collimator controls -> Collimator section
     How are controls unlocked.  Certain users?
  Spectrometer motion, fields, cryogenics -> spectrometer chapter + howtos?
  Beam current measurement
  Reset panel (Raspberry Pi)
  App developer howto (if we do one)

  jmenu

  Most controls maintained by accelerator controls group.  A few things
  done locally.  High Voltage, Beam current, Spectrometer EPICS gateway,
  reset panel.

} % \infolevtwo
