% Include here Hall dependent operation procedures
%
\newpage
\section{Special Procedures for \HALL}

There are no special operating procedures for \HALL{}.

% Include here experiment dependent operation procedures
%
\newpage
\section{Special Procedures for \EXPTS}\label{app:exp_req}

Each shift requires a shift leader and a polarized $^3$He target operator.
A third person on shift is extremely useful, but not required. The shift leader 
has the standard
duties of shift leader to ensure proper data taking, log all activity, and to fill out
the Beam Accounting form. The target operator should focus on the 
operation of the polarized $^3$He target. Target operator training is arranged by
Jian-ping Chen. The shift leader or third
shift worker will run the DAQ and online analysis codes, and fill out the shift checklist. 

This run period uses the ``standard'' Hall C equipment, 
a polarized $^3$He target, and the Moller polarimeter.
The use and safety procedures of the standard equipment are documented
in the Hall C Standard Equipment
Manual available from the Hall C web page.
The polarized $^3$He target will be used in Hall C for the first time.
The use and safety procedures of the polarized $^3$He target are 
documented in the TOSP (Target Operation Safety Procedures). 
The Moller polarimeter will be used by ``Moller experts'' to measure the beam
polarization. While used to be part of the Hall C standard equipment during the
6 GeV era, the Moller polarimeter will be used for the first time after the 12 GeV upgrade.
The use and safety procedures of the Moller polarimeter are
documented in the Moller OSP.
Both Target OSP and Moller OSP are available from the experimental webpage of \EXPTS. 

One special requirement of the polarized $^3$He target is the ``laser lockdown''
period. During this period, only personnel with polarized $^3$He target training or
laser safety training will be allowed
to access the hall. Details of the ``laser lockdown'' period and its safety and training
requirement are documented in the TOSP.

To summarize, the following OSPs are associated with \EXPTS:
\begin{itemize}
 \item Jefferson Lab Hall C Standard Equipment Manual;
 \item Polarized $^3$He Target OSP;
 \item Moller Polarimeter OSP.
\end{itemize}

\newpage
\section{Signature Sheets}

After reading this document, as well as TOSP, OSP of the Moller polarimetry,
ESAD, RSAD, and ERG, workers need to sign
the signature sheet located in the ``yellow binder'' of the experiment specific documents.
This binder can be found in the \HALL\ counting house and in the MCC.
